disturbance chronologies

### 2017-06-06 analysis/analysis_disturbance_chronos.Rmd
update titles
update

### Plot 
```{r}
# Plot mean value by year 
# dataframe for plot 
gc_todos <- c()

@@

gc_todos %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))
```

# Plot (correcting the scale)
```{r}

# Create a transformation scale 
# https://stackoverflow.com/questions/37446064/i-need-ggplot-scale-x-log10-to-give-me-both-negative-and-positive-numbers-as-o

@@

a <- gc_todos %>% 
  filter(site != 'gc_sj') %>% 
  ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray', width=.3, size=.2) +
  # scale_y_continuous(trans = pos_neg_log) +
  facet_wrap(~site, nrow = 2,
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low'))) +
                                # 'gc_sj' = 'San Juan'))) + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue', alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red', alpha=.4) + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

@@

## Númber of trees 
```{r}

@@

>>>>

### Plot (mean) 
```{r}
# Plot mean value by year 
# dataframe for plot 
gc_todos <- c()

@@

gc_todos %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('% GC (mean)') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))
```

### Plot (median) 
```{r}
gc_todos %>% ggplot(aes(x=year, y=gc_md)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('% GC (median)') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))
```

### Plot (correcting the scale) (mean)
```{r}
# Create a transformation scale 
# https://stackoverflow.com/questions/37446064/i-need-ggplot-scale-x-log10-to-give-me-both-negative-and-positive-numbers-as-o

@@

a <- gc_todos %>% 
  filter(site != 'gc_sj') %>% 
  ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray', width=.3, size=.2) +
  # scale_y_continuous(trans = pos_neg_log) +
  facet_wrap(~site, nrow = 2,
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low'))) +
                                # 'gc_sj' = 'San Juan'))) + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue', alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red', alpha=.4) + 
  ylab('% GC (mean)') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

@@

### Plot (correcting the scale) (median)
```{r}
c <- gc_todos %>% 
  filter(site != 'gc_sj') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) +
  # scale_y_continuous(trans = pos_neg_log) +
  facet_wrap(~site, nrow = 2,
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low'))) +
                                # 'gc_sj' = 'San Juan'))) + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue', alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red', alpha=.4) + 
  ylab('% GC (median)') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

d <- gc_todos %>% 
  filter(site == 'gc_sj') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  xlim(layer_scales(a)$x$range$range[1],layer_scales(a)$x$range$range[2]) +
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) +
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -100, 0, 100, 500)) +
  facet_wrap(~site, nrow = 2,
             labeller=as_labeller(c('gc_sj' = 'San Juan'))) + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue', alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red', alpha=.4) + 
  ylab('') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

grid.newpage()
grid.draw(rbind(ggplotGrob(c), ggplotGrob(d), size='last'))
```

## Number of trees with %GC > 50% (mean)
```{r}

@@

## Number of trees with %GC > 50% (median)
```{r}

  # Get n tree with GC positve upper treshold 
  n_pos <- gcdf %>% dplyr::filter(gc_median > th) %>% group_by(year) %>% summarise(n_pos = length(ntrees))

  # Get n tree with GC negative lower treshold 
  n_neg <- gcdf %>% dplyr::filter(gc_median < (-1*th)) %>% group_by(year) %>% summarise(n_neg = length(ntrees))

# Plot 
gc_trees %>% ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill='blue', colour='blue', stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill='red', colour='red', stat = "identity", position = "dodge") +
  facet_wrap(~site, nrow = 3, labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) + 
  scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  geom_line(aes(x=year, y=total_tree), colour = 'gray') + 
  theme_bw() + ylab('% trees GC > 50 % (median)') +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

# References
